Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-05-12 analysis/paper/paper_ana_20181122.Rmd
For review

  We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-member multiphysics ensemble. We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP’s prepBUFR files; AWS combining CONV and dense automatic surface weather station networks, SATWND, combining AWS with satellite-derived winds and RAD, including SATWND; and satellite radiances from different microwave and infrared sensors. We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation. We also ran ensemble forecasts initialized from each experiment and evaluated their skill to predict precipitation. We found that the hourly assimilation of the observations in AWS, SATWND, and RAD helped to improve the precipitation forecast.
journal: Atmospheric Research
#layout: authoryear,preprint,review,12pt
layout: final,5p,times,twocolumn,authoryear
address:
- code: UBA
  address: Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmósfera y los Océanos. Buenos Aires, Argentina.
- code: CIMA
  address: CONICET – Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmósfera (CIMA). Buenos Aires, Argentina.
- code: CNRS
  address: CNRS – IRD – CONICET – UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.
- code: SMN
  address: Servicio Meteorológico Nacional de Argentina.
- code: CONICET
  address: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas).
- code: INPE
  address: National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies.
- code: NCAR
  address: National Center for Atmospheric Research, Boulder, Colorado.
- code: Illinois
  address: Department of Atmospheric Sciences, University of Illinois at Urbana–Champaign, Urbana, Illinois.
bibliography: 
  - paper_ANA.bib 
  - packages.bib
csl: elsevier-harvard.csl
footnote:
- code: 1
  text: Corresponding Author
keywords: Regional Data Assimilation, Surface Obsevations, Satellite Observations 
numbersections: true
# header-includes: 
#  - \usepackage{gensymb}
#  - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
#  - \usepackage{chngcntr}
#  - \usepackage{natbib}
#  - \usepackage{lineno}
#  - \linenumbers 
---

@@

ggdraw(plot_grid(plot_grid(g1, g2, ncol = 2, rel_widths = c(1, 0.5), 
                           labels = c("a)", "b)"), label_size = 11), legend, 
                 ncol = 1, rel_heights = c(1, 0.05)))

@@

Where $P_{oi}$ is the fraction of grid points in the $i-th$ sampling area in which the observed accumulated precipitation is greater than a specified threshold. Following @maldonado2021, $P_{xi}$ is calculated from the ensemble probability precipitation over the same threshold in each grid point by averaging over the $i-th$ sampling area. 
The FSS was computed from the accumulated precipitation over 6 hr periods by adding the 1-hr accumulated precipitation forecasts over 6 consecutive assimilation cycles.

@@

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at <https://github.com/paocorrales/mesoda>. The derived data that support the findings of this study are also openly available in Zenodo at http://doi.org/[doi], reference number [reference number].

>>>>

  We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-member multiphysics ensemble. We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP’s prepBUFR files; AWS combining CONV and dense automatic surface weather station networks, SATWND, combining AWS with satellite-derived winds and RAD, including SATWND; and satellite radiances from different microwave and infrared sensors. We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation. We also ran ensemble forecasts initialized from each experiment and evaluated their skill to predict precipitation. We found that the hourly assimilation of the observations in AWS, SATWND, and RAD helped to improve the precipitation forecast.
journal: Atmospheric Research
layout: authoryear,preprint,review,12pt
#layout: final,5p,times,twocolumn,authoryear
address:
- code: UBA
  address: Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmósfera y los Océanos. Buenos Aires, Argentina.
- code: CIMA
  address: CONICET – Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmósfera (CIMA). Buenos Aires, Argentina.
- code: CNRS
  address: CNRS – IRD – CONICET – UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.
- code: SMN
  address: Servicio Meteorológico Nacional de Argentina.
- code: CONICET
  address: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas).
- code: INPE
  address: National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies.
- code: NCAR
  address: National Center for Atmospheric Research, Boulder, Colorado.
- code: Illinois
  address: Department of Atmospheric Sciences, University of Illinois at Urbana–Champaign, Urbana, Illinois.
bibliography: 
  - paper_ANA.bib 
  - packages.bib
csl: elsevier-harvard.csl
footnote:
- code: 1
  text: Corresponding Author
keywords: Regional Data Assimilation, Surface Obsevations, Satellite Observations 
numbersections: true
# header-includes: 
#  - \usepackage{gensymb}
#  - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
#  - \usepackage{chngcntr}
#  - \usepackage{natbib}
#  - \usepackage{lineno}
#  - \linenumbers 
---

@@

ggdraw(plot_grid(plot_grid(g1, g2, ncol = 2, rel_widths = c(1, 0.5), 
                           labels = c("a)", "b)"), label_size = 11), legend, 
                 ncol = 1, rel_heights = c(1, 0.08)))

@@

Where $P_{oi}$ is the fraction of grid points in the $i-th$ sampling area in which the observed accumulated precipitation is greater than a specified threshold. Following @roberts2020, $P_{xi}$ is calculated from the ensemble probability precipitation over the same threshold in each grid point by averaging over the $i-th$ sampling area. 
The FSS was computed from the accumulated precipitation over 6 hr periods by adding the 1-hr accumulated precipitation forecasts over 6 consecutive assimilation cycles.

@@

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at <https://github.com/paocorrales/mesoda>. The derived data that support the findings of this study are also openly available in Zenodo at http://doi.org/10.5072/zenodo.1060834, version 0.9.0.

### 2022-05-12 analysis/paper/paper_ana_20181122.tex
For review

\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc citation processing

% Pandoc header
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\begin{frontmatter}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{/home/paola.corrales/mesoda/analysis/figures/analysis_cycle} \caption{Figure 4. Diagram of the analysis cycles between 18 UTC Nov 20, and 12 UTC Nov 23 plus spin up period of 6 hours. The zoomed section shows the hourly assimilation that is performed within a one-hour centered window and new boundary conditions from GFS every 6 hours. The two IOP missions from the RELAMPAGO field campaign and the ensemble forecast initialized at 00 and 06 UTC Nov 22 are shown.}\label{fig:cycle}
\end{figure}

@@

Where \(P_{oi}\) is the fraction of grid points in the \(i-th\) sampling area in which the observed accumulated precipitation is greater than a specified threshold. Following Maldonado et al. (2021), \(P_{xi}\) is calculated from the ensemble probability precipitation over the same threshold in each grid point by averaging over the \(i-th\) sampling area.
The FSS was computed from the accumulated precipitation over 6 hr periods by adding the 1-hr accumulated precipitation forecasts over 6 consecutive assimilation cycles.

@@

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at \url{https://github.com/paocorrales/mesoda}. The derived data that support the findings of this study are also openly available in Zenodo at http://doi.org/{[}doi{]}, reference number {[}reference number{]}.

@@

>>>>

\documentclass[authoryear,preprint,review,12pt]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

\usepackage{lineno} % add

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO campaign},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\begin{frontmatter}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/analysis_cycle} \caption{Figure 4. Diagram of the analysis cycles between 18 UTC Nov 20, and 12 UTC Nov 23 plus spin up period of 6 hours. The zoomed section shows the hourly assimilation that is performed within a one-hour centered window and new boundary conditions from GFS every 6 hours. The two IOP missions from the RELAMPAGO field campaign and the ensemble forecast initialized at 00 and 06 UTC Nov 22 are shown.}\label{fig:cycle}
\end{figure}

@@

Where \(P_{oi}\) is the fraction of grid points in the \(i-th\) sampling area in which the observed accumulated precipitation is greater than a specified threshold. Following Roberts et al. (2020), \(P_{xi}\) is calculated from the ensemble probability precipitation over the same threshold in each grid point by averaging over the \(i-th\) sampling area.
The FSS was computed from the accumulated precipitation over 6 hr periods by adding the 1-hr accumulated precipitation forecasts over 6 consecutive assimilation cycles.

@@

A version-controlled repository of the code used to create this analysis, including the code used to download the data can be found at \url{https://github.com/paocorrales/mesoda}. The derived data that support the findings of this study are also openly available in Zenodo at http://doi.org/10.5072/zenodo.1060834, version 0.9.0.

@@

\leavevmode\hypertarget{ref-roberts2020}{}%
Roberts, B., Gallo, B.T., Jirak, I.L., Clark, A.J., Dowell, D.C., Wang, X., Wang, Y., 2020. What Does a Convection-Allowing Ensemble of Opportunity Buy Us in Forecasting Thunderstorms? Weather and Forecasting 35, 2293--2316. doi:\href{https://doi.org/10.1175/WAF-D-20-0069.1}{10.1175/WAF-D-20-0069.1}
